---
title: "SasQ R Utility"
author: "Ron Schweßinger"
date: "4 Dezember 2015"
output:
  pdf_document:
    toc: yes
  html_document:
    toc: yes
---


# Introduction
>>Insert tiny Introduction

# Initial
First of all *source* the the SasQ Functions distributet in *functions_sasq_r_utility.R*
```{r, tidy=TRUE}
source("/home/ron/fusessh/Sasquatch_offline/Sasquatch/R_utility/functions_sasq_r_utility.R")
```

We first set some parameters like the tissue and the fragmentation type to select the desired data.
```{r}
tissue <- "human_erythroid_hg18"

frag.type <- "DNase"
```

And we set the path to the database directory
```{r, tidy=TRUE}
data.dir <- file.path("/home/ron/fusessh/database_assembly/idx_correct_assembly/human", frag.type)
```
```{r, echo=FALSE, tidy=T}
print(data.dir)
```

and we also initialize the file path structure where to reach a precalculated vocabulary file if present.
```{r, tidy=TRUE}
vocab.file <- paste0(data.dir,tissue,"/vocabulary_", tissue,".txt")
```

```{r, echo=FALSE, tidy=TRUE}
print(vocab.file)
```





